\bf Manuscript Draft

### 2023-11-07 Manuscript/Manuscript.tex
Added table to manuscript

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor = blue}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{lipsum}
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}

@@

\setlength{\linewidth}{5in}

@@

\if0\blind
{
  \title{\bf Manuscript Draft}
  \author{Zoe Macris\\
  University of Connecticut Department of Statistics
\date{December 2023}
  \maketitle}

@@

\section{Data}
\label{sec:data}
\section{Methods}
\label{sec:methods}

\section{Simulation}
\label{sec:somulation}

@@

@@

\bibliography{FinalCitations}

>>>>

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor = blue}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{lipsum}
\usepackage{siunitx}
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}

@@

\setlength{\linewidth}{3in}

@@

\if0\blind
{
  \title{\bf Manuscript Draft}
  \author{Zoe Macris}
\date{December 2023}
  \maketitle}

@@

\section{Data}
\label{sec:data}

\section{Methods}
\label{sec:methods}

@@

The paper by Mateo-Babiano takes the approach of using by Spearman correlation to analyse the effects of various cycling measures on usage, as can be seen in ~\ref{fig:Mateo-Babiano}

\begin{table}[tbp]
\label{fig:Mateo-Babiano}
\centering
\caption{Length of bikeway by bikeway type in Brisbane and CityCycle areas. Spearman correlation of station usage and infrastructure type: from Mateo-Babiano paper}
\begin{tabular}{l*{5}{p{2cm}}}
\toprule
{Infrastructure type} & {Length Brisbane Area (km)} & {Lenth in CityCycle area (km)} & {Correlation coefficent} & {P-value}\\
\midrule
Shared Pathway & 327.9 & 18.0 & 0.42 & <0.01 \\
Bicycle Lane & 186.7 & 21.3 & 0.03 & 0.69 \\
Bicycle Awareness Zone (BAZ) & 303.7 & 40.3 & -0.07 & 0.39 \\
Bicycle Path & 23.9 & 2.6 & 0.27 & <0.01 \\
Bicycle Route (BAZ) & 76.9 & 8.2 & 0.13 & 0.11 \\
Connect & 19.5 & 5.0 & 0.16 & 0.049 \\
Informal Off Road & 65.8 & 4.6 & 0.00 & 0.98 \\
Informal On Road & 18.2 & 4.1 & -0.13 & 0.12 \\
Separated Pathway & 1.8 & 1.3 & 0.29 & <0.0 \\
\bottomrule
\end{tabular}
\end{table}

@@

\bibliography{Citations}
